---
title: "Premier League Shiny App"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, eval = FALSE)
```

This Shiny App looks at Premier League data from the 2013-2014 season up to the 2018-2019 season. It analyses the data through Data Exploration, k Means Clusters, k-Nearest Neighbors, and Random Forests. 

There are three data sets utilized in this analysis.

  1. Relegations
  
  2. Soccer Data

  3. Income PL

Please note that some data sets use club and some use team. Club and team are interchangeable and will be used as such throughout the content. 

#### Available through GitHub:
```{r}
shiny::runGitHub("Premier League", "lcwitek")
```

#### Also available through shinyapps.io:
[Premier League Shiny App](https://lcwitek.shinyapps.io/ST558-Final-Project/)


## Packages Required for app.R
```{r}
library(shiny)
library(shinydashboard)
library(dplyr)
library(tidyverse)
library(randomForest)
library(knitr)
library(caret)
library(tree)
library(janitor)
library(glmnet)
library(splines)
library(pls)
library(boot)
library(plotly)
library(ggplot2)
library(cluster)
library(factoextra)
library(grid)
library(class)
library(cowplot)
library(e1071)
```
